%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Industry Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
{Backend Developer} % Job title
{101edu, Inc.} % Organization
{Remote Work} % Location
{Aug. 2016 - Jan. 2017,\ \ Sep. 2017 - Dec. 2017} % Date(s)
{
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item Implemented RESTful API server for Chem101 mobile applications and web application using Spring framework (DI, Boot, Data, Security, Web).
		\item Built and deployed overall service infrastructure utilizing several AWS stack (including EC2, S3, CloudFront, Route 53, CodePipieline, CodeBuild, and IAM), focusing on high-availability, fault tolerance, and auto-scaling.
		\item Integrated external services such as Stripe payment processing and AWS SNS push notifications.
	\end{cvitems}
}

%---------------------------------------------------------
  \cventry
    {Software Engineer Intern} % Job title
    {Facebook, Inc.} % Organization
    {Menlo Park, CA} % Location
    {May 2017 - Sep. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      	\item Worked on development of Facebook’s internal version of Apache Hive and focused on performance.
      	\item Identified scope for improvement in core join logic of Hive and redesigned it and the components around it. When tested with join queries, observed \textasciitilde 14\% overall performance improvement.
      	\item Produced readable code and provided a cleaner and strictly typed abstraction while still reducing query times.
      	\item Identified and fixed multiple long-lived correctness bugs.
      	\item Collected statistics to better understand the nature of the queries and shared findings with team to help guide future projects.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineering Intern} % Job title
    {Microsoft Corp.} % Organization
    {Seattle, WA} % Location
    {May 2016 - Aug. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Added framework functionality to help customers customize their user interface without needing to modifying code.
        \item Identified a development issue and created a Chrome extension to reduce development time for the Microsoft Dynamics CRM team.
        \item Aquired an understanding about development of scalable enterprise application and good practices to reduce maintenance costs.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Research Engineer} % Job title
    {ezDI, Inc.} % Organization
    {Ahmedabad, India} % Location
    {Apr. 2015 - Aug. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      	\item Lead a team of 3 interns (undergraduate and PhD) and a full time engineer to develop an information retrieval system called Codebook.
      	\item Codebook is currently used by hospitals in US to lookup medical codes by entering medical terms, synonyms and multiple user customizable abbreviations.
      	\item Designed the system architecture, RESTful web services, and security module.
      \end{cvitems}
      %\begin{cvsubentries}
      %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
      %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
      %\end{cvsubentries}
    }

%---------------------------------------------------------
\end{cventries}
