%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Developer} % Affiliation/role
    {Spire Course Checker} % Organization/group
    {Amherst, MA} % Location
    {Jun. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
      	\item Noticed an issue with the lack of waitlist for course registeration at UMass Amherst.
        \item Created a course checker in Python that used Selenium to check for open courses periodically and to notify a student about it.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Team Leader and Developer} % Affiliation/role
    {Nectarime} % Organization/group
    {Amherst, MA} % Location
    {May 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item Lead a team for CS 326 Web Programming Project to enable sharing of files from mobile to public computer through QR scan.
        \item Created the base framework using NodeJS and React, and integrated services such as Dropbox and Google Drive.
        \item Used web sockets and peer to peer communication along with SSL to allow secure, rapid file sharing.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Developer} % Affiliation/role
    {{\fontfamily{ptm}\selectfont \LaTeX } Bot for Slack} % Organization/group
    {Amherst, MA} % Location
    {Nov. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item Identified problems with sharing of problems involving special symbol over Slack group and limitations of existing solutions.
        \item Created a Slack Bot written in NodeJS that replied with images produced from {\fontfamily{ptm}\selectfont \LaTeX } code sent with the ability to process edited messages.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Developer} % Affiliation/role
    {Contextr} % Organization/group
    {Amherst, MA} % Location
    {Oct. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item Developed a context-aware text suggestion engine that suggested text based on the document context and related documents.
        \item Used data scrapped from web pages online to create contextual Markov chains and used them to rank next word suggestions.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Developer} % Affiliation/role
    {Dynapodd} % Organization/group
    {Ahmedabad, India} % Location
    {Jan. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item Dynapodd is an example based query and update system as an extension for Hibernate ORM and Spring Data MongoDB.
        \item Created using Java Reflection API to ease the development of backend for my startup, Phostcard.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Founder and Developer} % Affiliation/role
    {GoPapers.net} % Organization/group
    {Ahmedabad, India} % Location
    {Apr. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item Application to allow quick access to past papers for Cambridge International Examninations.
        \item 40,000 users from 140 countries have used this web application.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Creator} % Affiliation/role
    {Home Automation System} % Organization/group
    {Ahmedabad, India} % Location
    {Feb. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item Worked on several automation projects using Arduino and microcontrollers, along with a variety of sensors and components.
        \item Designed a Bluetooth IR relay device that would allow TV and AC control from phone.
        \item Created an app to dim the lights in the house, and control the fan speed over WiFi.
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
